Global code motion of congruent instructions

### 2017-04-18 paper.tex
formatting

\begin{verbatim}
int doCodeHoisting()
  // Collect hoistable candidates
  For each value number VN with 2 or more instructions (I1, I2, ..., Ik)
    sort the instructions according to DFSIn numbers
    if first two I1, I2 are hoistable and if they are downward-safe at hoist-point
       and if they are profitable to be hoisted at hoist-point
      proceed to check ability to hoist of subsequent instruction with same VN
    else
      proceed to check if I2 and I3 (if available) can be hoisted

  // Do the code hoisting and update statistics
  For each set of instructions (I1, ..., Ik) with same VN that can be hoisted:
    move the first one I1 to the hoist-point
    update the use of all other candidates (I2, ..., Ik) to refer to I1
    remove all other instructions (I2, ..., Ik)
    if I1 has memory references (a load, store, call, etc.)
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics

  return number of hoisted instructions
\end{verbatim}

\newpage
After no more candidates are hoistable, sinking is performed. Sinking is only
performed once because currently there are very few sinkable candidates
(Table~\ref{tab:code-motion-metric}) as SimplifyCFG of LLVM (which runs before
\GCM{}) has a code-sinking which already sinks several instructions.

>>>>

\begin{verbatim}
int doCodeHoisting() // Find hoistable candidates and do hoisting
  For each value number VN with 2 or more instructions (I1, I2, ..., Ik)
    sort the instructions according to DFSIn numbers
    if first two I1, I2 are hoistable and if they are downward-safe at hoist-point
          and if they are profitable to be hoisted at hoist-point
      proceed to check the ability to hoist subsequent instruction with same VN
    else
      proceed to check if I2 and I3 (if available) can be hoisted
  For each set of instructions (I1, ..., Ik) with same VN that can be hoisted:
    move the first one I1 to the hoist-point
    update the use of all other candidates (I2, ..., Ik) to refer to I1
    remove all other instructions (I2, ..., Ik)
    if I1 has memory references (a load, store, call, etc.)
      update MemorySSA of I1 and others to point to the MemorySSA reference of I1
      remove MemorySSA reference of all others which were deleted
    update statistics
  return number of hoisted instructions
\end{verbatim}

%\newpage
After no more candidates are hoistable, sinking is performed. Sinking is only
performed once because currently there are very few sinkable candidates
(Table~\ref{tab:code-motion-metric}) as SimplifyCFG of LLVM (which runs before
\GCM{}) has a code-sinking which already sinks several instructions.
